Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-18 providence/sections/model.tex
alpha and section not Section
Lots of changes

We now summarize the model drawing largely from the notation and terminology of \cite{usenix_minerva,arxiv_athena,simulations,bravo}. The model is related work and not claimed to be original to this work.

An audit $\mathcal{A}$ is a function that takes as input the sample of ballots and outputs either (1) \emph{Correct: stop the audit} or (2) \emph{Undetermined: sample more ballots}. As described in the introduction, we ignore a third option of moving to a hand count, leaving that decision to election officials. We provide more context on this in section \ref{sec:related}, on related work.

\BRAVO and \Minerva are modeled as binary hypothesis tests where the null hypothesis $H_0$ corresponds to a tied election and the alternative hypothesis $H_a$ to an election tally as announced. 
(When the number of ballots is odd, $H_0$ corresponds to the announced loser winning by one ballot.)
Thus the null hypothesis is the outcome distinct from the announced one which is most difficult to detect; the probability of failing to detect it, given that the null hypothesis is true, is the worst case such probability and should be below the risk limit \cite{Bayesian-RLA}.

\begin{definition}[Risk Limiting Audit ($\alpha$-RLA)]
An audit $\mathcal{A}$ is a Risk Limiting Audit with 
risk limit $\alpha$ iff for sample $X$
$$
Pr[\mathcal{A}(X) 
= \text{Correct} \,|\, H_0]\le \alpha
$$
\end{definition}

@@

@@

>>>>

%We now summarize the model drawing largely from the notation and terminology of \cite{usenix_minerva,arxiv_athena,simulations,bravo}. The model is related work and not claimed to be original to this work.

%An audit $\mathcal{A}$ is a function that takes as input the sample of ballots and outputs either (1) \emph{Correct: stop the audit} or (2) \emph{Undetermined: sample more ballots}. As described in the introduction, we ignore a third option of moving to a hand count, leaving that decision to election officials. This is standard in the literature, see, for example, \cite{bravo}. We provide more detail on the use of this option in section \ref{sec:related}, on related work.

\BRAVO and \Minerva are modeled as binary hypothesis tests where the null hypothesis $H_0$ corresponds to a tied election and the alternative hypothesis $H_a$ to an election tally as announced. 
(When the number of ballots is odd, $H_0$ corresponds to the announced loser winning by one ballot.)
%Thus the null hypothesis is the outcome distinct from the announced one which is most difficult to detect; the probability of failing to detect it, given that the null hypothesis is true, is the worst case such probability and should be below the risk limit \cite{Bayesian-RLA}.

%\begin{definition}[Risk Limiting Audit ($\alpha$-RLA)]
%An audit $\mathcal{A}$ is a Risk Limiting Audit with 
%risk limit $\alpha$ iff for sample $X$
%$$
%Pr[\mathcal{A}(X) 
%= \text{Correct} \,|\, H_0]\le \alpha
%$$
%\end{definition}

@@

\BRAVO is an instance of Wald's Sequential Probability Ratio Test (SPRT) \cite{wald}. Applying the general SPRT to RLAs, there would be a third output, {\em Full Manual Hand Count}, in addition to {\em Correct} and {\em Undetermined}. The test requires an additional error parameter $\beta$ (of audit error when the outcome is correct): the probability of requiring a (unnecessary) hand count when the outcome is correct. The test is:
\begin{equation}
    \mathcal{A}(X) =  \left\{ \begin{array}{ll} \emph{Correct} & ~\sigma(k, p_a, p_0, n) 
        \geq \frac{1-\beta}{\alpha}\\ \\ \\
       \emph{Hand~Count} & ~\sigma(k, p_a, p_0, n) 
        < \frac{\beta}{1-\alpha}\\ \\ \\
        \emph{Undetermined} & ~else 
    \end{array}
    \right .
    \label{eqn:wald}
\end{equation}

An example of the above use is \cite{RLA}. In the more recent literature, for example \cite{bravo}, ballot polling audits do not include this possibility (i.e. they set $\beta=0$) in order to give maximum flexibility to election officials in choosing when to proceed to a full manual count. 
%In principle, the stopping condition could indicate a third option too: (c) the audit proceeds to a full manual hand count. This option is generally not incorporated \cite{bravo}. 
% Election officials would typically decide to perform a full manual hand count if the audit does not stop in spite of drawing a large number of ballots, typically over multiple rounds.

A manual hand count presents significant logistical challenges. Left to election officials, the decision would be influenced by the certification deadline, the estimated number of human hours required for another round, the logistical costs of a full hand count, and the impact of any decision on citizen confidence. The only disadvantage of leaving the decision to election officials would be when the outcome were incorrect, and election officials would continue drawing rounds hoping that they would not need to escalate to a full hand count. Audits going towards statutory or legal requirements would need to be completed by the certification deadline; this provides an incentive to go to a hand count. Pilot audits, performed after certification, usually end after a single round or fixed number of rounds, providing a measured risk (the statistical p-value) at the end of the round, and no decision regarding a full hand count needs to be made. A better workload model would enable a better determination of when election officials are better off stopping than drawing more ballots

@@

Note that $\tau$ depends only on the most recent cumulative votes for the winner, $k_j$ and not on older values. Here, if we were to condition the ratio on the vector of cumulative winner votes $\bm{k_{j-1}}$, or, equivalently, on the most recent cumulative winner votes ${k_{j-1}}$, we would get the binomial distributions and be running a new first round each time.

Notice that the ratios for \BRAVO and \Minerva are for two candidates. Audits of multiple-candidate contests are treated as multiple audits of the pairwise contest between the announced winner and all other candidates.

The {\em margin}, given a contest and two candidates, is the difference between the votes received by each as a fraction of the total number of votes.

### 2023-02-18 providence/sections/prov.tex
alpha and section not Section
Lots of changes

In this section we introduce the stopping condition of \Providence and prove some properties.

Recall that the proof that the \Minerva audit is risk-limiting assumes that the round schedule of \Minerva is predetermined and that, in particular, an adversarial auditor cannot determine the next round size after drawing a sample (we termed such an adversary a weak adversary in section \ref{sec:adv}). This presents difficulties because a non-adversarial election official might want to draw a small next round if the current sample comes close to satisfying the risk limit. Because the \Minerva round size is predetermined, however, the election official would be required to draw a larger round size than necessary for the sample. Conversely, if the current sample is not at all close to satisfying the risk limit, it would be advantageous to draw a larger round than the predetermined round size. Thus it would be advantageous to have an RLA with \Minerva's efficiency advantages in the face of an adversarial auditor who could choose next round sizes after drawing the sample (we termed such an adversary a strong adversary). This would enable honest participants to better plan audits.

Before proceeding to define the audit \Providence which is an RLA in the presence of the stronger adversary, we formalize the notions of weak and strong adversaries introduced in section \ref{sec:adv}.

\begin{definition}[Weak Adversary]
A {\emph weak adversary} may choose the first and consequent round sizes as a pre-determined function of audit parameters. That is, the $j^{th}$ round size is a function $$n_j(\alpha, p_a, p_0)$$ determined before the audit begins. 
\end{definition}

\begin{definition}[Strong Adversary]
A {\emph strong adversary} may choose any round size as any function of audit parameters and all preceding samples. That is, the first round size is a function 
$$n_1(\alpha, p_a, p_0),$$
and for all rounds $j\ge 2$, the round size is a function
$$n_{j}(\alpha, p_a, p_0, \bm{k_{j-1}}, \bm{n_{j-1}})$$ The functions $n_j$, $j \geq 1$ may be chosen at any time before the $j^{th}$ round begins. 
\end{definition}

Before defining \Providence, we give some intuition for how it is designed to avoid the problem of \Minerva.

For any ballot polling audit, in round $j$, designed to stop for some value of $K_j$, however large $K_j$ is, there is, in general, a probability, however small, that the value of $K_j$ has resulted from an underlying incorrect election outcome. Thus, corresponding to each such value of $K_j$, a risk---probability that the audit will stop given that the outcome is incorrect---is incurred. To obtain the total risk for the round, one adds the risks corresponding to each value of $K_j$ for which the audit can stop, weighted by the probability of drawing that value of $K_j$. The stopping condition may provide relationships among the various quantities.

In \Minerva, the stopping condition relates the weighted average of the risks to the weighted average of the stopping probabilities over all values of $K_j$, for a given round size. Separate relationships between risk and stopping probability are not available for individual values of $K_j$. If the next round size depends on $K_j$, expressions relating the risks are not available, and so we are not able to say if \Minerva is an RLA in this case, or if it is vulnerable to an adversary choosing round sizes \cite{usenix_minerva, arxiv_athena}.

In \Providence, we choose a stopping condition that applies separately to the risk and stopping probabilities for each value of $K_j$, avoiding the problem of \Minerva, and allowing for optimal round size choices, which depend on the drawn sample. 
The \Providence audit is risk-limiting even if a strong adversarial auditor determines round sizes after drawing the sample, and next round size computations may use knowledge of the current sample.

@@

Notice that \Providence requires the computation of $\tau_j$ for $j=1$ and no other values of $j$. The value of $\tau_1$ is simply the ratio of the the tails of the binomial distributions (the distributions are binomial because the auditing is with replacement) for the two hypotheses and can be fairly efficiently computed. The computation of $\tau_j$ for $j \geq 2$, as required in \Minerva, relies on the convolution of two probability distribution functions and is hence computationally considerably more expensive. Lesser computational complexity makes audit planning and analysis using simulations as in Section~\ref{sec:workload} more feasible.

@@

\subsection{Risk-Limiting Property: Proof}
\label{sec:proof}
We now prove that \Providence is risk-limiting against a strong adversary using lemmas from basic algebra which are given in Appendix~\ref{sec:proofs}.

\begin{theorem}
\label{thm:minerva2_is_rla_new}
$(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence is an
$\alpha$-RLA in the presence of a strong adversary.
\end{theorem}
\begin{proof}
Let $\mathcal{A}=(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence.
Let $\bm{n_j}$ be the cumulative round sizes used in this
audit, with corresponding cumulative tallies of
ballots for the reported winner $\bm{k_j}$.
For round $j=1$, by Definitions \ref{def:minervatwo}
and \ref{def:minerva_ratio}, we see that
the $\mathcal{A}=\text{Correct}$ (the audit stops) only when
$$
\tau_1(k_{1},p_a,p_0,n_1)\\
=\frac{Pr[K_{1} \geq k_{1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{1} \mid H_0, n_1]}
\ge \frac{1}{\alpha}.
$$
By Lemma \ref{lemma:minerva2_kmin_exists} and Definition \ref{def:kmin}, there is 
a value $k_{min,1} = k^{p_a, p_0, \alpha, 0}_{min, 1, 0, n_1}$ such that 
$$
\frac{Pr[K_{1} \geq k_{1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{1} \mid H_0, n_1]}
\ge
\frac{Pr[K_{1} \geq k_{min,1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{min, 1} \mid H_0, n_1]}
\ge 
\frac{1}{\alpha}.
$$

For any round $j\ge 2$, by Definition \ref{def:minervatwo}
and Lemma \ref{lemma:minerva2_kmin_exists},
$\mathcal{A}=\text{Correct}$ (the audit stops) if and only if
\begin{equation*}
\begin{aligned}
\omega_{j}(k_{j}, k_{j-1}, p_a, p_0, n_{j}, n_{j-1}, \alpha )\triangleq\\
\sigma(k_{j-1},p_a,p_0,n_{j-1})\cdot \tau_1(k_{j}-k_{j-1},p_a,p_0,n_j-n_{j-1})
\ge \frac{1}{\alpha}.
\end{aligned}
\end{equation*}
%Let $d_j=k_j-k_{j-1}$ be shorthand for the new draw.
%could do this for simpler notation^
By Lemma \ref{lemma:any_ratio_is_sigma_simple}
and Definition \ref{def:minerva_ratio}, this is equivalent to
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}
$$$$\ge \frac{1}{\alpha}.
$$
By Lemma~\ref{lemma:minerva2_kmin_exists} and Definition~\ref{def:minervatwo},
we see that there exists a $k_{min, j} = k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j}  \leq k_j$ 
%$k_{min, j}\le k_j$ 
for which
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}\ge
$$
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]} 
$$$$
\ge 
\frac{1}{\alpha}
$$
%Equivalently,
%$$
%\frac{Pr[K_{j} \ge k_{min, j}\wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_a]}{Pr[K_{j}\ge k_{min, j} \wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_0]}\ge \frac{1}{\alpha}.
%$$
%Taking the sum over all possible rounds and corresponding preceding values
%of $k$, we get
% Taking the sum over all possible audit histories, we get
The above may be rewritten as
\begin{equation*}
\begin{aligned}
\sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_0, n_{j-1}, n_{j}] \leq \\
\alpha \sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_a, n_{j-1}, n_{j}]
\end{aligned}
\end{equation*}
The left hand side above is the probability of stopping in the $j^{th}$ round and $K_{j-1} = k_{j-1}$, given the null hypothesis, which is smaller than $\alpha$ times the same probability given the alternate hypothesis. 
For different possible values of $k_{j-1}$, different round sizes $n_j$ can be used, and this same relationship will hold. 
That is, the relationship holds even if the values of $n_{j}$ depend on $k_{j-1}$, if $n_j$ is a function $n_j(\alpha, p_0, p_1, \bm{k_{j-1}}, \bm{n_{j-1}})$.\footnote{\Minerva enforces a similar relationship between risk and stopping probability but does so at the level of the round rather than for each individual value of $K_{j-1}$. By enforcing this relationship for each value of $K_{j-1}$, \Providence is resistant to a strong adversary.}

>>>>

In this section we describe the adversarial model and introduce the stopping condition of \Providence, proving some of its properties.

%Recall that the proof that the \Minerva audit is risk-limiting assumes that the round schedule of \Minerva is predetermined and that, in particular, an adversarial auditor cannot determine the next round size after drawing a sample (we termed such an adversary a weak adversary in section \ref{sec:adv}). This presents difficulties because a non-adversarial election official might want to draw a small next round if the current sample comes close to satisfying the risk limit. Because the \Minerva round size is predetermined, however, the election official would be required to draw a larger round size than necessary for the sample. Conversely, if the current sample is not at all close to satisfying the risk limit, it would be advantageous to draw a larger round than the predetermined round size. Thus it would be advantageous to have an RLA with \Minerva's efficiency advantages in the face of an adversarial auditor who could choose next round sizes after drawing the sample (we termed such an adversary a strong adversary). This would enable honest participants to better plan audits.

%Before proceeding to define the audit \Providence which is an RLA in the presence of the stronger adversary, we formalize the notions of weak and strong adversaries introduced in section \ref{sec:adv}.

\subsection{Adversarial Model for RLAs}
\label{sec:adv}
Detailed descriptions of best practices for post-election audits may be found in \cite{best-practices,why-and-how}. For our purposes, we will assume that best practices are followed: the paper trail consists of hand-marked paper ballots and is secured; a public compliance audit is carried out before the RLA to ensure that the processes for securing the paper trail were followed; voter authentication and registration processes are verified, and only legitimate voters cast no more than a single vote each; the risk-limiting audit is public. We will further assume that all software used in the RLA is open source and well-defined, so its output may be reproduced and thus verified by an observer wishing to do so with their own software.

Referring to the ballot polling audit steps described in section \ref{sec:polling}, we further assume that the ballot manifest is verified by the compliance audit; a secure PRNG is used; the seed is generated uniformly at random in a public process; the process of locating ballots is publicly observable and the located ballots can be viewed by the public. Because the PRNG is well-defined, as is the stopping condition, we may assume that the stopping condition is correctly computed, because it can be checked by the public through knowledge of the seed and the drawn ballots. Thus the only variable is round size.

We define a {\em weakly round-choosing adversary} as one who can choose the first and subsequent round sizes before the audit begins and a {\em strongly round-choosing adversary} as one who can choose any round size at any time (before, of course, that particular round begins). In particular, a strongly round-choosing adversary may use information about the sample drawn thus far to decide the next round size, but a weakly round-choosing adversary may not.

\begin{definition}[Weakly Round-Choosing Adversary]
A {\emph weakly round-choosing adversary} may choose the first and consequent round sizes as a pre-determined function of audit parameters. That is, the $j^{th}$ round size is a function $$n_j(\alpha, p_a, p_0, ballot\_manifest)$$ determined before the audit begins. 
\end{definition}

\begin{definition}[Strongly Round-Choosing Adversary]
A {\emph strongly round-choosing adversary} may choose any round size as any function of audit parameters and all preceding samples. That is, the first round size is a function 
$$n_1(\alpha, p_a, p_0, ballot\_manifest),$$
and for all rounds $j\ge 2$, the round size is a function
$$n_{j}(\alpha, p_a, p_0, ballot\_manifest, \bm{k_{j-1}}, \bm{n_{j-1}})$$ The functions $n_j$, $j \geq 1$ may be chosen at any time before the $j^{th}$ round begins. 
\end{definition}

\subsection{The Intuition Behind the Properties of \Providence}
Before defining \Providence, we give some intuition for how it is designed to avoid the problem of \Minerva.

Consider any ballot polling audit in round $j$, designed to stop for some value of $K_j=k_j$ smaller than the round size. In general, if $k_j$ is large, the probability of this value of $K_j$ given a correct outcome, $Pr[K_j = k_j \mid H_1]$, is larger than the corresponding risk---$Pr[K_j = k_j \mid H_0]$, the probability of this value of $K_j$ given a tie. The risk is generally not zero, however. Thus, corresponding to each such value of $K_j$, a risk is incurred. To obtain the total risk for the round, one adds the risks corresponding to each value of $K_j$ for which the audit can stop, weighted by the probability of drawing that value of $K_j$. The stopping condition may provide relationships among the various quantities. To obtain the risk of the entire audit, one sums the risks of each round.

In \Minerva, the stopping condition relates the weighted average of the risks to the weighted average of the stopping probabilities over all values of $K_j$, for a given round size. Separate relationships between risk and stopping probability are not available for individual values of $K_j$. If the next round size depends on $K_j$, expressions relating the risks are not available, and we are not able to obtain an expression bounding the sum of the risks across rounds. Thus we are not able to determine if \Minerva is an RLA in this case, or if it is vulnerable to the strongly round-choosing adversary \cite{usenix_minerva, arxiv_athena, alpha}.

In \Providence, we choose a stopping condition that applies separately to the risk and stopping probabilities for each value of $K_j$, avoiding the problem of \Minerva, and allowing for optimal round size choices, which depend on the drawn sample. 
The \Providence audit is risk-limiting even if a strongly round-choosing adversarial auditor determines round sizes after drawing the sample, and next round size computations may use knowledge of the current sample.

@@

Notice that \Providence requires the computation of $\tau_j$ for $j=1$ and no other values of $j$. The value of $\tau_1$ is simply the ratio of the the tails of the binomial distributions (the distributions are binomial because the auditing is with replacement) for the two hypotheses and can be fairly efficiently computed. The computation of $\tau_j$ for $j \geq 2$, as required in \Minerva, relies on the convolution of two probability distribution functions and is hence computationally considerably more expensive. Smaller computational complexity makes audit planning and analysis using simulations as in section~\ref{sec:workload} more feasible.

@@

\subsection{Risk-Limiting Property: Proof}
\label{sec:proof}
We now prove that \Providence is risk-limiting against a strongly round-choosing adversary using lemmas from basic algebra which are given in Appendix~\ref{sec:proofs}.

\begin{theorem}
\label{thm:minerva2_is_rla_new}
$(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence is an
$\alpha$-RLA in the presence of a strongly round-choosing adversary.
\end{theorem}
\begin{proof}
Let $\mathcal{A}=(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence.
Let $\bm{n_j}$ be the cumulative round sizes used in this
audit, with corresponding cumulative tallies of
ballots for the reported winner $\bm{k_j}$.
For round $j=1$, by Definitions \ref{def:minervatwo}
and \ref{def:minerva_ratio}, we see that
the $\mathcal{A}=\text{Correct}$ (the audit stops) only when
$$
\tau_1(k_{1},p_a,p_0,n_1)\\
=\frac{Pr[K_{1} \geq k_{1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{1} \mid H_0, n_1]}
\ge \frac{1}{\alpha}.
$$
By Lemma \ref{lemma:minerva2_kmin_exists} and Definition \ref{def:kmin}, there is 
a value $k_{min,1} = k^{p_a, p_0, \alpha, 0}_{min, 1, 0, n_1}$ such that 
$$
\frac{Pr[K_{1} \geq k_{1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{1} \mid H_0, n_1]}
\ge
\frac{Pr[K_{1} \geq k_{min,1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{min, 1} \mid H_0, n_1]}
\ge 
\frac{1}{\alpha}.
$$

For any round $j\ge 2$, by Definition \ref{def:minervatwo}
and Lemma \ref{lemma:minerva2_kmin_exists},
$\mathcal{A}=\text{Correct}$ (the audit stops) if and only if
\begin{equation*}
\begin{aligned}
\omega_{j}(k_{j}, k_{j-1}, p_a, p_0, n_{j}, n_{j-1}, \alpha )\triangleq\\
\sigma(k_{j-1},p_a,p_0,n_{j-1})\cdot \tau_1(k_{j}-k_{j-1},p_a,p_0,n_j-n_{j-1})
\ge \frac{1}{\alpha}.
\end{aligned}
\end{equation*}
%Let $d_j=k_j-k_{j-1}$ be shorthand for the new draw.
%could do this for simpler notation^
By Lemma \ref{lemma:any_ratio_is_sigma_simple}
and Definition \ref{def:minerva_ratio}, this is equivalent to
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}
$$$$\ge \frac{1}{\alpha}.
$$
By Lemma~\ref{lemma:minerva2_kmin_exists} and Definition~\ref{def:minervatwo},
we see that there exists a $k_{min, j} = k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j}  \leq k_j$ 
%$k_{min, j}\le k_j$ 
for which
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}\ge
$$
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]} 
$$$$
\ge 
\frac{1}{\alpha}
$$
%Equivalently,
%$$
%\frac{Pr[K_{j} \ge k_{min, j}\wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_a]}{Pr[K_{j}\ge k_{min, j} \wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_0]}\ge \frac{1}{\alpha}.
%$$
%Taking the sum over all possible rounds and corresponding preceding values
%of $k$, we get
% Taking the sum over all possible audit histories, we get
The above may be rewritten as
\begin{equation*}
\begin{aligned}
\sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_0, n_{j-1}, n_{j}] \leq \\
\alpha \sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_a, n_{j-1}, n_{j}]
\end{aligned}
\end{equation*}
The left hand side above is the probability of stopping in the $j^{th}$ round and $K_{j-1} = k_{j-1}$, given the null hypothesis, which is smaller than $\alpha$ times the same probability given the alternate hypothesis. 
For different possible values of $k_{j-1}$, different round sizes $n_j$ can be used, and this same relationship will hold. 
That is, the relationship\footnote{\Minerva enforces a similar relationship between risk and stopping probability but does so at the level of the round rather than for each individual value of $K_{j-1}$. By enforcing this relationship for each value of $K_{j-1}$, \Providence is resistant to a strongly round-choosing adversary.} holds even if the values of $n_{j}$ depend on $k_{j-1}$, if $n_j$ is a function $n_j(\alpha, p_0, p_1, \bm{k_{j-1}}, \bm{n_{j-1}})$.
